The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-23 EducProposal.Rmd
Update EducProposal.Rmd

@@

@@

@@

@@

As mentioned above, we will need to control for the economic outlook at the time of data collection about entrepreneurship characteristics. We will also need to control for nine key entrepreneurship conditions as defined in the [National Experts Survey (NES)](http://www.gemiran.ir/sec/gem/?@=28) that may affect the rate of entrepreneurship. These nine conditions are the following:

@@

@@

1. Return on Investment: Assigning a future Euro value to a present-day investment. This may require the use of a social discount rate, but will also need to consider the potential GDP increase brought about by improved education policies.

2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach in measuring this factor.

3. Positive reinforcement: Again even if this is not easy to quantify, we will attempt to compute as an index and characterize it on a scale.

>>>>

#### Hypothesis

@@

##### Entrepreneurship as a dependent variable

@@

##### Self-confidence as the key explanatory variable

@@

##### Social inclusion as a complementary explanatory variable

@@

##### Other classic determinants of entrepreneurship as control variables

We will obviously need to control for the economic outlook at the time of data collection about entrepreneurship characteristics. We will also need to control for nine key entrepreneurship conditions as defined in the [National Experts Survey (NES)](http://www.gemiran.ir/sec/gem/?@=28) that may affect the rate of entrepreneurship. These nine conditions are the following:

@@

##### Process

@@

1. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach in measuring this factor.

2. Positive reinforcement: Again even if this is not easy to quantify, we will attempt to compute an index and characterize it on a scale.

3. Culture: Key concept broadly understood here as the ensemble of beliefs, values, norms and practices of a given society.

4. Education: Here education is understood as the process of apprenticeship that takes place in schools throughout compulsory years (from the age of 6 to 16). Thus we examine the average potential effect of these years of "shaping" on individuals throughout the entire population of a country.

5. Return on Investment: Assigning a future Euro value to a present-day investment. This may require the use of a social discount rate, but will also need to consider the potential GDP increase brought about by improved education policies.
